ICS Phenotyping

### 2019-09-12 ICS_Cleaning.Rmd
fix the TH2 definition because it wasn't strict enough

---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE )
```

@@

      TH1_TbetCXCR3=  rowSums(CD4_phenotype[,grep("TH1_t_._3_.", names(CD4_phenotype))]),
      TH1_TbetCCR4=  rowSums(CD4_phenotype[,grep("TH1_t_._._4", names(CD4_phenotype))]),
      TH1_GATA3CXCR3=  rowSums(CD4_phenotype[,grep("TH1_._g_3_.", names(CD4_phenotype))]),
      TH1_GATA3CCR4=  rowSums(CD4_phenotype[,grep("TH1_._g_._4", names(CD4_phenotype))]),
      TH2_TbetCXCR3=  rowSums(CD4_phenotype[,grep("TH2_t_._3_.", names(CD4_phenotype))]),
      TH2_TbetCCR4=  rowSums(CD4_phenotype[,grep("TH2_t_._._4", names(CD4_phenotype))]),
      TH2_GATA3CXCR3=  rowSums(CD4_phenotype[,grep("TH2_._g_3_.", names(CD4_phenotype))]),
      TH2_GATA3CCR4=  rowSums(CD4_phenotype[,grep("TH2_._g_._4", names(CD4_phenotype))]),
      ifng_TbetCXCR3=  rowSums(CD4_phenotype[,grep("ifng_t_._3_.", names(CD4_phenotype))]),
      ifng_TbetCCR4=  rowSums(CD4_phenotype[,grep("ifng_t_._._4", names(CD4_phenotype))]),
      ifng_GATA3CXCR3=  rowSums(CD4_phenotype[,grep("ifng_._g_3_.", names(CD4_phenotype))]),
      ifng_GATA3CCR4=  rowSums(CD4_phenotype[,grep("ifng_._g_._4", names(CD4_phenotype))]),
      tnfa_TbetCXCR3=  rowSums(CD4_phenotype[,grep("tnfa_t_._3_.", names(CD4_phenotype))]),
      tnfa_TbetCCR4=  rowSums(CD4_phenotype[,grep("tnfa_t_._._4", names(CD4_phenotype))]),
      tnfa_GATA3CXCR3=  rowSums(CD4_phenotype[,grep("tnfa_._g_3_.", names(CD4_phenotype))]),
      tnfa_GATA3CCR4=  rowSums(CD4_phenotype[,grep("tnfa_._g_._4", names(CD4_phenotype))]),

>>>>

---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE )

@@

      TH1_TbetCXCR3=  rowSums(CD4_phenotype[,grep("TH1_t_._3_.", names(CD4_phenotype))]),
      TH1_TbetCCR4=  rowSums(CD4_phenotype[,grep("TH1_t_._._4", names(CD4_phenotype))]),
      TH1_GATA3CXCR3=  rowSums(CD4_phenotype[,grep("TH1_._g_3_.", names(CD4_phenotype))]),
      TH1_GATA3CCR4=  rowSums(CD4_phenotype[,grep("TH1_._g_._4", names(CD4_phenotype))]),
            TH1_GATA3notCCR4=  rowSums(CD4_phenotype[,grep("TH1_._g_._x", names(CD4_phenotype))]),
      TH2_TbetCXCR3=  rowSums(CD4_phenotype[,grep("TH2_t_._3_.", names(CD4_phenotype))]),
      TH2_TbetCCR4=  rowSums(CD4_phenotype[,grep("TH2_t_._._4", names(CD4_phenotype))]),
      TH2_GATA3CXCR3=  rowSums(CD4_phenotype[,grep("TH2_._g_3_.", names(CD4_phenotype))]),
      TH2_GATA3CCR4=  rowSums(CD4_phenotype[,grep("TH2_._g_._4", names(CD4_phenotype))]),
      ifng_TbetCXCR3=  rowSums(CD4_phenotype[,grep("ifng_t_._3_.", names(CD4_phenotype))]),
      ifng_TbetCCR4=  rowSums(CD4_phenotype[,grep("ifng_t_._._4", names(CD4_phenotype))]),
      ifng_GATA3CXCR3=  rowSums(CD4_phenotype[,grep("ifng_._g_3_.", names(CD4_phenotype))]),
      ifng_GATA3CCR4=  rowSums(CD4_phenotype[,grep("ifng_._g_._4", names(CD4_phenotype))]),
      tnfa_TbetCXCR3=  rowSums(CD4_phenotype[,grep("tnfa_t_._3_.", names(CD4_phenotype))]),
      tnfa_TbetCCR4=  rowSums(CD4_phenotype[,grep("tnfa_t_._._4", names(CD4_phenotype))]),
      tnfa_GATA3CXCR3=  rowSums(CD4_phenotype[,grep("tnfa_._g_3_.", names(CD4_phenotype))]),
      tnfa_GATA3CCR4=  rowSums(CD4_phenotype[,grep("tnfa_._g_._4", names(CD4_phenotype))]),

### 2019-09-12 ICS_Phenotyping.Rmd
fix the TH2 definition because it wasn't strict enough

```{r}
test<-mutate_TB(filter(DF, !is.na(TH1_GATA3)))
test2<-melt(test, id.vars=c("Donor", "TB", "SM", "Stim"), measure.vars = grep("TH1_._._._.", names(DF)))
test2<-filter(test2, variable!="TH1_x_x_x_x")
test2$variable<-gsub("TH1_", "", test2$variable)
ggplot(test2, aes(x=variable, y=value, fill=TB, alpha=SM))+
    geom_boxplot()+
    scale_alpha_manual(values=c(0.5,1))+
    scale_fill_manual(values =c("#2166ac", "#b2182b"))+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=8)+
    theme(legend.position="none")+
    theme(plot.title = element_text(hjust = 0.5)) +
    labs(title="Lineage Marker Expression on Mtb-Specific TH1 CD4+ T cells",
         y="Frequency of Marker+ Mtb-Specific T cells")+
    coord_cartesian(ylim=c(0,10))
kable(xtabs(~TB+SM, test))
```

>>>>

```{r}
test<-mutate_TB(filter(DF, !is.na(TH1_GATA3)))
test2<-melt(test, id.vars=c("Donor", "TB", "SM", "Stim"), measure.vars = grep("TH1_._._._.", names(DF)))
test2<-filter(test2, variable!="TH1_x_x_x_x")
test2$variable<-gsub("TH1_", "", test2$variable)
ggplot(test2, aes(x=variable, y=value, fill=TB, alpha=SM))+
    geom_boxplot()+
    scale_alpha_manual(values=c(0.5,1))+
    scale_fill_manual(values =c("#2166ac", "#b2182b"))+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=8)+
    theme(legend.position="none")+
    theme(plot.title = element_text(hjust = 0.5)) +
    labs(title="Lineage Marker Expression on Mtb-Specific TH1 CD4+ T cells",
         y="Frequency of Marker+ Mtb-Specific T cells")+
    coord_cartesian(ylim=c(0,20))
kable(xtabs(~TB+SM, test))
```
